%! Author = mycroft
%! Date = 2022-06-29

% Preamble
\documentclass[12pt,twocolumn]{article}

% Packages
\usepackage{amsmath}
\usepackage[body={8in, 8in},top=1cm]{geometry}
\usepackage{enumitem}
\usepackage{acbl2022cc}  % for suits, etc.

\makeatletter

\def\@maketitle{%
\par\center{\textbf{\@title} -- \@date}%
\par%
\par}

\makeatother

\title{Notes for Michael Farebrother -- Ellen Kuiper: K/S system}

% Document
\begin{document}
    \maketitle
\begin{scriptsize}
    \begin{enumerate}
        \item 1 NT is 12--14 all seats, all vulnerabilities.
         We upgrade especial 11s (Michael more than Ellen).
        \begin{enumerate}[label*=\arabic*.,nosep]
            \item We do \textbf{not} play Stayman over 1 NT.  2\,\bc\ is Keri: a puppet to 2\,\rd.
            This is forced; there is no other systemic response to 2\,\bc.
            Responder's rebids:
            \begin{description}
                \item [Pass] Weak with Diamonds
                \item [2\,\rh] INV with 4 \textbf{or 5} hearts (but see 1 NT--2\,\rd below)
                \item [2\,\bs] INV with 4 \textbf{or 5} spades
                \item [2 NT] GF Puppet Stayman.
                 Specialized responses.
                \item [3 m] INV with 6+ of the minor
                \item [3 M] GF, 5+ \textbf{diamonds} and 5 of the major
                \item [3 NT] Mild \textbf{diamond} slam try.
                 Usually 5332 or 6322.
            \end{description}
            \item We do \textbf{not} play Gerber.
            Over 1 NT and 2 NT, 4 m transfers to corresponding major, 4 M is to play.
            \item Other special responses over 1NT:
            \begin{description}
                \item [1 NT--2\,\rd] hearts, but very rarely 4: if responder rebids 2\,\bs,
                      they are INV with both majors: 5\,\bs--5\,\rh, 5\,\bs--4\,\rh\ or 4\,\bs--4\,\rh, but not 4\,\bs--5\,\rh.
                \label{item:4-hearts}
                \item [1 NT--2\,\bs] Range ask.
                2 NT is minimum, 3\,\bc\ is maximum.
                Responder's suit rebid is RKC (3NT: xx, then 4\,\bc: "don't care, Keycard.")
                \item [1 NT--3 suit] GF, 3-suited, short in \textbf{the next suit up}.
                 Bidding the short suit shows no wasted values and max, 3NT promises good stoppers.
                \item [1 NT--4 NT] 0123 Blackwood.
                 \textbf{Not} quantitative.
            \end{description}
            \item Over interference:
            \begin{itemize}
                \item Over double (all seats, all meanings), our runout is "2\,\bc\ Scramble":
                \begin{itemize}
                    \item Keri and Transfers are off.
                    Almost all calls, including Pass and XX, are natural and to play.
                    XX sets a force through 2\,\rd.
                    \item The exception is 2\,\bc, which is "Natural", but 1+.
                     This call is to play undoubled.
                      If doubled:
                    \begin{itemize}
                        \item Opener will pass with 3+ clubs, or bid her lowest 4-card suit.
                        \item Responder will pass with 4+ clubs, or bid her lowest 4-card suit.
                        \item Runs are also to play unless doubled, or if a 7 card fit is found.
                        Further bidding as above.
                    \end{itemize}
                \end{itemize}
                \item Over 2\,\bc\ overcalls (again, no matter what they mean), systems on, X is Keri.
                \item Over 2\,\rd\ or higher, Lebensohl, double of shown suit is Negative.
                \item When dealing with a forcing "X or Y" interference, we may choose to bid directly or allow you to clarify and Lebensohl over that.
            \end{itemize}
        \end{enumerate}
        \item Carding:
        \begin{itemize}[nosep]
            \item Leads: standard 4\textsuperscript{th} best, but A for Attitude, K for Kount throughout.
            \item Signals: We play Upside Down Attitude, Count \textbf{and Suit Preference}.
            Suit preference is the default secondary signal, and we play Trump Suit Preference.
            \item Against NT, we play Reverse Smith Echo (if attitude is not known to opening leader's suit, signal to trick 2 is (upside down) attitude in leader's suit, not a signal about declarer's suit).
        \end{itemize}
        \newpage
        \item We play Power Doubles and 1NT Overcall for takeout:
        \begin{enumerate}[label*=\arabic*.,nosep]
            \item (1 suit)--X shows "any" 15+, but because we will pass for penalty with much weaker trumps than "normal", with a singleton, it's about 17, and with a void, about 19.
            \begin{itemize}
                \item It frequently shows a strong NT, with or without stoppers.
                \item Next suit up (exc.\ 1\,\bs--X) is an artificial negative, 0--bad 4 any.
                \item Non-jump bids are natural and about good 4--bad 8.
                \item 1 NT is good 4--7 basically balanced, and implies, but does not promise, a stopper.
                \item Cuebid is good 8+, GF
                \item Jump bids are good suits.
            \end{itemize}
            \item (1 suit)--1 NT is takeout, usually 8--14 HCP, guaranteeing 3+cards in all unbid suits.
            \begin{itemize}
                \item With perfect shape, especially NV in 2nd, could be on 6 (Open chart only).
                \item With a singleton (16) or void (18) in bid suit, we may overcall 1NT with more than 14 HCP\@.
                \item We are fairly aggressive with this call, and can do it with 5 card suits; but with 4333, we will be on the top of the range.
                \item Pass is rare, but possible.
                \item New suits are natural and to play.
                \item Cuebid is Stayman-esque, and could be the start of a INV+ sequence.
                \item Jump bids are preemptive [Exception: INV at unfavourable].
                \item If 1 NT is doubled, new suits are to play (usually 5+), XX shows 4 cards in the highest unbid suit, and pass is any other (\textbf{not} to play).
            \end{itemize}
        \end{enumerate}
        \item We play Fit Jump Shifts (9+ cards in bid suit and partner's, about limitish values) even by unpassed hand without competition.
        \item In situations where we show two known or one known and one unknown suit, 2 NT is strong and asking, and cheapest unknown suit is pass/correct.
         This applies to:
        \begin{itemize}[nosep]
            \item Woolsey overcalls of 1 NT
            \item Michaels cuebids
        \end{itemize}
        \item Our preempt style is more aggressive than most, heavily dependent on vulnerability and seat:
        \begin{itemize}[nosep]
            \item NV first seat weak twos could be Jxxxxx.
             Second seat vulnerable, the minimum is probably KJ9xxx.
            \item Similar arguments apply to 3- and 4-major bids, and 3NT (4 level minor preempt, \textbf{not} gambling).
            \item However, 3\,\bc/\rd\ in first and second seat are "happy to put dummy down in 3NT", and 4\,\bc/\rd\ is Namyats (solid 8 and nothing, or 1-Loser 8 with an outside A or K).
            \item We are similarly aggressive with jump overcalls and preemptive raises.
        \end{itemize}
    \end{enumerate}
\end{scriptsize}
\end{document}
